Title Goes Here

### 2019-03-24 analysis/paper/paper.Rmd
read in data
updates for plot

```{r demo, eval = FALSE}
1 + 1
```

@@

```{r get-data, eval = FALSE}
# Note the path that we need to use to access our data files when rendering this document
my_data <- readr::read_csv(here::here('analysis', 'data', 'raw_data', 'my_csv_file.csv'))
```

>>>>

```{r read-in-the-data, eval = FALSE}
library(here)
kwl_upper <- readxl::read_excel(here("analysis", "data", "raw_data", "Kiwulan_Ornament_Upper.xlsx"))
```

@@

```{r get-data, eval = FALSE}
# summarise the ornaments by layers
library(tidyverse)
library(ggplot2)

# L5 and L6 represent pre-European contact period, 
# L4 was the time of European contact, and 
# L2 and L1 was the period of Chinese contact.

ornaments_period <- 
kwl_upper %>% 
  filter(!is.na(`6-layers`)) %>% 
  mutate(period = case_when(
    `6-layers` %in% 1:2 ~ "Chinese Contact",
    `6-layers` == 4 ~ "European Contact",
    `6-layers` %in% 5:6 ~ "Before European Contact",
     TRUE ~ "other"
  )) %>% 
  filter(period != "other")

# need to reorder, try https://forcats.tidyverse.org/reference/index.html
# reorder factor for categories (by frequency) and period (manually)

ornaments_count <-
  ornaments_period %>% 
  filter(!is.na(`6-layers`)) %>% 
  group_by(period, Categories) %>%
  count() %>% 
  ungroup() %>% 
  mutate(Categories = fct_lump(as.factor(Categories), n = 5)) %>% 
  mutate(Categories = fct_reorder(Categories, n))

ggplot(transform(ornaments_count,
                 period = factor(period, 
                                     levels = c("Before European Contact", 
                                                "European Contact", 
                                                "Chinese Contact")))) +
  geom_col(aes(Categories, n)) +
  facet_wrap(~ period) +
  coord_flip() +
  labs(y = "Frequency")
```
